Finite-state morphological transducers for three Kypchak languages

### 2013-10-20 kipchak-lrec-2013/kipchak-paper.tex
kaz and tat population estimates
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@48156 72bbbca6-d526-0410-a7d9-f06f51895060

\subsection{Kazakh}
Kazakh has approximately 12 million speakers

\subsection{Tatar}
Tatar has approximately  million speakers

\subsection{Kumyk}
Kumyk has approximately  million speakers

>>>>

\subsection{Kazakh}
Kazakh is primarily spoken in Kazakhstan, where it is the national language, sharing official status with Russian as an official language.  Large communities of native speakers also exist in China, neighbouring Central-Eurasian republics, and Mongolia.  Estimates of the total number of speakers range from 8 million \citep{ethnologue} to 11 million \citet{encyclopedin} people.

\subsection{Tatar}
Tatar is spoken in and around Tatarstan by approximately 5.4 million people \citep{ethnologue}. It is co-official with Russian in Tatarstan --- a republic within Russia.  A majority of native speakers of both languages are bilingual in Russian. %, and the standard varieties our system FIXMEs are written in Cyrillic.

\subsection{Kumyk}
Kumyk has approximately 430 thousand speakers \cite{ethnologue}
